Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-09 Grassmannian_cells.tex
Notation changes in section 4

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
        \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
      \end{equation}
    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,I}:\tilde P_{m+1}\to \tilde P_{m+1-k,\ui}^I$ satisfying:
      \[\tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
      \qquad\text{and}\qquad
    \tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from Lemma~\ref{le:properties}.5.

  These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
\qed\end{proof}

@@

Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

We will apply these results in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.1 provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \eta_m:\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above for any fixed $\tbfe$:
\begin{equation}
  \label{eq:truncated CC}
  \Psi=\Psi^{\eta_m}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \xi_m:\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
\begin{equation}
  \label{eq:truncated CC2}
  \Phi=\Phi^{\xi_m}:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a non-empty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.4.
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

  Now consider $U\subset\tilde P_{m,j}$ with $U\in\Phi^{-1}(V,W)$.
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    \Ext(\tilde P_{m+1}^I,V)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,W)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\ar[r]\ar[d] & 0 \\
    0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/V\big)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W).\]

  If $W=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)=\varnothing$.

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is surjective.
  By Lemma~\ref{le:properties}.4 and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is non-empty in this case.
\qed\end{proof}

>>>>

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{& \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[dl] \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
        \tilde P_{m+1}^J \ar^{\tilde\pi_{m+1}^{J,\{i\}^c}}[r] & \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
      \end{equation}
    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
      \[\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
      \qquad\text{and}\qquad
    \tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that we may take $J=\varnothing$ in Lemma~\ref{le:truncated quotients}.3 but the conditions impose $I\ne\varnothing$.
\end{remark}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangles is immediate from Lemma~\ref{le:properties}.5.

  These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}\]
  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
\qed\end{proof}

@@

Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(F,G)\cong\mathbb{A}^{\dim\Hom(G,M/F)}$.
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\prec\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\succ\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

We will apply these results in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.3 provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \eta_m:\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above for any fixed $\tbfe$:
\begin{equation}
  \label{eq:truncated CC}
  \Psi=\Psi^{\eta_m}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \xi_m:\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
\begin{equation}
  \label{eq:truncated CC2}
  \Phi=\Phi^{\xi_m}:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a non-empty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
    \item The fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(F)=(F,0)$, i.e.\ $F$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $F\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,F)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r] & 0}.\]
  But note that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& F\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & F'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.4.
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,F)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)=0$.
  This argument can be reversed and thus (1) holds.

  Now consider $F\subset\tilde P_{m,j}$ with 
  \[\Phi(F)=(S,T)\in\Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).\]
  This gives rise to the following commutative diagram:  
  \[\xymatrix{
    \Ext(\tilde P_{m+1}^I,S)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,T)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)\ar[r]\ar[d] &  \Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r]\ar[d] & \Ext(\tilde P_{m+1}^I,\tilde K_m)\ar[r]\ar[d] & 0\\
    \Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\ar[r]\ar[d] &\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\ar[r]\ar[d] & 0 \\
    0&0&0&}\]
  By Corollary~\ref{cor:perpendicular}, we have $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$ and so $\Ext\big(\tilde P_{m+1}^I,\tilde P_m(I,j)/S\big)=0$ as well.
  This yields the isomorphisms
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Ext(\tilde P_{m+1}^I,\tilde K_m)\quad\text{and}\quad\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T).\]

  If $T=0$, we get an isomorphism $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$ and by part (1) we must have an empty fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)=\varnothing$.

  If $T\neq 0$, $\tilde K_m/T$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/T)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/T$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(Z,\tilde K_m/T)\to\Hom(\tilde K_m,\tilde K_m/T)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/T)\to\Ext(Z,\tilde K_m/T)\]
  is surjective.
  By Lemma~\ref{le:properties}.4 and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/T)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/F)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/T)$ must be zero as well.
  By part (1) we see that the fiber $\Psi^{-1}(F,\tilde P_{m+1}^I)$ is non-empty in this case.
\qed\end{proof}
